---
title: "dnaseqtool"
author: "Perezhil Nagendirakumar"
date: "4/26/2022"
output: html_document
---
# dnaseqtool package :

dnaseqtool is a package developed for the nucleotide sequence analysis especially DNA sequence containing Adenine "A", Thymine "T" , Guanine "G" and Cytosine "C" basepairs retrieved from database like NCBI using accession id to get some meaningful insights of the sequence.

 **Retrival of sequence from database** :
 
I tested dnaseqtool package to analyse the dengue virus sequence retrived from NCBI database using  rentrez package ::entrez_fetch function . Dengue virus causes Dengue fever, which is classified as a neglected tropical disease by the World Health Organization (WHO), is classified by any one of four types of Dengue virus: DEN-1, DEN-2, DEN-3, and DEN-4. The NCBI accessions for the DNA sequences of the DEN-1, DEN-2, DEN-3, and DEN-4 Dengue viruses are
1.NC_001477
2.NC_001474
3.NC_001475
4.NC_002640

 
```{r}
#Retrieving the nucleotide sequence of den4 using its "NC_002640" accession id in ncbi database and
#storing it in a variable getncbiseq
library(seqinr)
getncbiseq <- rentrez::entrez_fetch(db = "nucleotide",
                                    id = "NC_002640",    
                                     rettype = "fasta")
getncbiseq
```
```{r}
#writing it in fasta format 
write(getncbiseq,
      file="deng4.fasta")
```
```{r}
# reading the fasta file and storing in a variavle called dengue and to access read.fasta seqinr package is required 
library(seqinr)
dengue<-read.fasta(file ="deng4.fasta", as.string = TRUE, forceDNAtolower = FALSE)
dengue
dengueseq<-dengue[[1]]
dengueseq

```
**Analysis of the nucleotide sequence** :

1.**complementary dna synthesis**:

cdna function generates a complementary dna for the input fasta file dengueseq by replacing Adenine "A" with Thymine"T"and Guanine "G" with Cytosine "C" and vice versa .
```{r}
dnaseqtool:::cdna(dengueseq)

```

2.**calculate AT **:

AT function calculates percentage of Adenine and Thymine nucleotide basepair composition in the input fasta file dengueseq 
```{r}
dnaseqtool:::AT(dengueseq)
```

3. **calculate GC **

GC function calculates percentage of Guanine and Cytosine nucleotide basepair composition in the input fasta file dengseq. 

```{r}
dnaseqtool:::GC(dengueseq)
```

4. **sliding window plot **

sliding plot function gives a graphical/visual representation of nucleotides basepair for the dengue sequence . To do that I have included the first 210 nucleotide of the dengueseq. It requires Zoo package . 
```{r}
library(zoo)
slidinginput<-("AGTTGTTAGTCTGTGTGGACCGACAAGGACAGTTCCAAATCGGAAGCTTGCTTAACACAGTTCTAACAGT
TTGTTTGAATAGAGAGCAGATCTCTGGAAAAATGAACCAACGAAAAAAGGTGGTTAGACCACCTTTCAAT
ATGCTGAAACGCGAGAGAAACCGCGTATCAACCCCTCAAGGGTTGGTGAAGAGATTCTCAACCGGACTTT")
dnaseqtool:::slidingplot(10,slidinginput)
